Peering Through Censorship:\\Tackling Internet Censorship Using P2P Networking

### 2023-05-18 paper.tex
Writing, some refs

\section{Prior proxying theory and techniques}

Most proxying techniques fall into one of three broad categories: looking like an unknown protocol, mimicing an existing protocol, or using an existing protocol as intended. Of these, mimicry was eliminated as a functional technique. Houmansadr et al established requirements that a mimicry system must meet to succeed - the imitated protocol must be mimiced in full, the imitation protocol must react properly to errors and network conditions, the imitation protocol must have traffic typical of the imitated protocol, and the imitation protocol must imitate artifacts from implementations of the imitated protocol properly.\cite{parrot} They continued by showing that none of the cutting edge mimicry protocols of the time were able to fulfill these requirements.\footnote{The authors explore SkypeMorph, StegoTorus, and CensorSpoofer - they quickly find passive attacks for these transports.\cite{skypemorph}\cite{stegotorus}\cite{censorspoofer}\cite{parrot}} The authors finally show that even with the initial attacks they find, hypothetical, improved transports that patch those would still fail as there are attacks that could not be prevented when imitating a proprietary protocol. The authors have a damning conclusion that has held until today: "unobservability by imitation is a fundamentally flawed approach, unlikely to ever suceed due to the daunting list of reqirements that an imitator must satisfy. The failure of all proposed [imitation] circumvention systems to achiever unobservability confirms this conclusion."\cite{parrot}

[TODO: Break down into high bandwidth/low bandwidth]

@@

\subsection{Unknown Protocols}

\subsubsection{OBFS and Scramblesuit}

@@

[TODO: Mention this w/ raven, bridgedb, etc]

@@

[Important to hit: recent OBFS entropy attack, Iran study that shows slowdown, China, DNS/IP censorship, DNSSEC failure]

@@

\subsection{The bridge distribution problem}

@@

Earlier, [TODO: xref] we discussed a variety of censorship circumvention systems. Observing how and why each of these work, and the drawbacks associated with each of them will allow us to formulate goals we wish to achieve, working techniques we may use, and a theory for our systems function. We present a short summary of previous systems in [TODO: xref table], comparing and contrasting their successful techniques and transports, and their individual drawbacks.

@@

We see that existing systems are limited by at least one of the following:
\begin{itemize}
  \item The bridge distribution problem [TODO: Xref]
  \item Scalability
  \item Deployment difficulty
  \item Low bandwidth
\end{itemize}

>>>>

\section{Prior proxying theory and techniques}
\label{prior}

Most proxying techniques fall into one of three broad categories: looking like an unknown protocol, mimicing an existing protocol/service, or using an existing protocol/service as intended. Of these, mimicry was eliminated as a functional technique. Houmansadr et al established requirements that a mimicry system must meet to succeed - the imitated protocol must be mimiced in full, the imitation protocol must react properly to errors and network conditions, the imitation protocol must have traffic typical of the imitated protocol, and the imitation protocol must imitate artifacts from implementations of the imitated protocol properly.\cite{parrot} They continued by showing that none of the cutting edge mimicry protocols of the time were able to fulfill these requirements.\footnote{The authors explore SkypeMorph, StegoTorus, and CensorSpoofer - they quickly find passive attacks for these transports.\cite{skypemorph}\cite{stegotorus}\cite{censorspoofer}\cite{parrot}} The authors finally show that even with the initial attacks they find, hypothetical, improved transports that patch those would still fail as there are attacks that could not be prevented when imitating a proprietary protocol. The authors have a damning conclusion that has held until today: "unobservability by imitation is a fundamentally flawed approach, unlikely to ever suceed due to the daunting list of reqirements that an imitator must satisfy. The failure of all proposed [imitation] circumvention systems to achiever unobservability confirms this conclusion."\cite{parrot}

Beyond mimicry, most systems fall into either looking like an unkown protocol, or using an existing protocol as intended. We can also break down proxying techniques into low-bandwidth and high-bandwidth techniques. High-bandwidth, on it's own, is generally preferred to lower bandwidth, however, in censorship circumvention other tradeoffs exist - most notably, the cost of censoring many low-bandwidth channels is higher than many high bandwidth channels. These channels frequently use an existing protocol/service as intended, which means that censoring these channels may require taking down a high value service, e.g. if a circumvention system uses email effectively, it may only be possible to block by blocking email. We discuss several examples of both low and high bandwidth channels in the following sections. [TODO: Discuss the notion of signalling]

[TODO: Discuss DPI, xref real world section]

@@

\subsection{High-bandwidth channels}

Several high-bandwidth channels have been created, and at least two are in active use in real world situations. We first discuss channels that attempt to look like an unknown protocol, and then discuss ones that attempt to use existing protocols and services as intended.

\subsubsection{Unknown protocols}

As censorship apparati developped, DPI began being used. DPI caused issues for several protocols - as it was able to selectively censor unencrypted or partially encrypted data streams based on parameters that a censor sets. [TODO: xref DPI] OBFS2 was developped by the Tor project to begin providing protection to access to the Tor network.\cite{obfs2} This protocol added an obfuscation layer, which encrypted the full stream and made the stream look like a stream of unknown bytes, in order to get past basic DPI. Obfs2 was vulnerable however, as a passive MITM [TODO: make sure this is defined earlier] could listen and decrypt the transport.\cite{obfs3} In addition to DPI, active probing arose as a technique that earlier circumvention techniques could be detected (and subsequently blocked) using. Active probing involves an adversary sending data of their choice to a server of their choice, and observing the response. They may potentially continue probing depending on the response. [TODO: Give an example] obfs2 was vulnerable to active probes as well.\footnote{And, indeed, it was actively probed by China.\cite{TODO https://gitlab.torproject.org/legacy/trac/-/issues/8591}}

obfs3 was developped to patch issues with obfs2. The main issue it addressed was the ability to perform passive decryption of the flow. This was done by using a custom Diffie-Hellman handshake.\cite{obfs3} obfs3 was still vulnerable to active probing.\cite{scramblesuit} Scramblesuit was designed to address this flaw, as well as several other identified tells of obfs3.\cite{scramblesuit} Scramblesuit defined a strong adversary, similar to the one proposed in this paper, and aimed to tackle active probing while also introducing basic traffic shaping via padding as well as inter-arrival times - introducing the concept of a polymorphic traffic shape for a protocol.\footnote{Polymorphic shaping is a promising defense for circumventors. The basic concept is that if every server has a unique traffic shape, then even if an adversary is able to identify a single server effectively, they will be unable to use that information in blocking other servers. This concept has not been fully exploited by a published circumvention technique at the time of writing.} Scramblesuit introduced the addition of a shared secret distributed \emph{out-of-band} to enable these improvements. From a usability and deployment standpoint, this was not a drastic departure from previous techniques: the older transports required basic info such as the bridge's IP address to be transmitted out of band, and this simply extended the amount of out-of-band information that needs to be transmitted by several characters.\footnote{Usability and deployment were specific considerations in the development of Scramblesuit - it was designed to be used by Tor and in the real world.\cite{scramblesuit}} Scramblesuit consists of two phases: a uniform diffie-hellman key exchange, and then a data exchange phases.

Scramblesuit performed some evaluation, however, they identified a key problem with evaluating circumvention techniques that affects all protocols that attempt to look like unknown protocols: evaluation is very difficult due to the lack of good datasets and effective experimental setups. The authors opted to show that the transport differs from the carried protocol (in this case, Tor).\cite{scramblesuit} Regardless, Scramblesuit became widely deployed.\footnote{Notably, inter-arrival time manipulation was off by default and could optionally be turned on. This was because inter-arrival time manipulation introduced significant overhead. With hindsight, we have seen other issues with Scramblesuit and have not seen issues caused by inter-arrival time manipulation being disable. These other issues are discussed directly below.}

Scramblesuit had notable overhead from it's andshake phases. The UniformDH used modlar exponentiation, which is an expensive operation.\cite{obfs4} Additionally, Scramblesuit was vulnerable to some MitM attacks if the attacker knew the shared secret.\cite{obfs4} obfs4 replaced the UniformDH with use of Tor's ntor handshake, with obfuscation done by Elligator 2.\cite{obfs4} obfs4 is still in use today, and is one of the main two circumvention techniques used for circumventing censorship in the Tor browser.

[TODO: Wang et al, new censorship]

@@

[TODO: Mention this w/ sweet, raven, bridgedb, etc]

@@

[TODO: Important to hit: recent OBFS entropy attack, Iran study that shows slowdown, China, DNS/IP censorship, DNSSEC failure]

@@

\subsection{The bridge distribution problem}
\label{distribution}

@@

In Section \ref{prior} we discussed a variety of censorship circumvention systems. Observing how and why each of these work, and the drawbacks associated with each of them will allow us to formulate goals we wish to achieve, working techniques we may use, and a theory for our systems function. We present a short summary of previous systems in [TODO: xref table], comparing and contrasting their successful techniques and transports, and their individual drawbacks.

@@

We see that existing systems are limited by at least one of the following:
\begin{itemize}
  \item The bridge distribution problem (\emph{see} Section \ref{distribution})
  \item Scalability
  \item Deployment difficulty
  \item Low bandwidth
\end{itemize}
